\thema

### 2019-09-10 Docs/paper/extended_abstract.tex
translate table content of template

\begin{center}
	\begingroup
	\renewcommand*{\arraystretch}{1}
	\rowcolors{2}{white}{white}
	{\makeatletter	
		\begin{tabular}{p{3.2cm}p{9.6cm}}
			Thema: & \thema \\
			& \\
			Teammitglieder: & \verfasserA, \verfasserB, \verfasserC, \verfasserD \\
			& \\
			Betreuer: & \hoschschule \newline \institut \newline \prueferA \\
			& \\
		\end{tabular}

>>>>

\begin{center}
	\begingroup
	\renewcommand*{\arraystretch}{1}
	\rowcolors{2}{white}{white}
	{\makeatletter	
		\begin{tabular}{p{3.2cm}p{9.6cm}}
			Topic: & \thema \\
			& \\
			Team members: & \verfasserA, \verfasserB, \verfasserC, \verfasserD \\
			& \\
			Advisor: & \hoschschule \newline \institut \newline \prueferA \\
			& \\
		\end{tabular}
